---
title: "p8105_hw5_rh2916"
author: "Rui Huang"
date: "November 1, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(purrr)
```


Problem 1

### Start with a dataframe containing all file names
```{r}
df = as.data.frame(list.files(path = "./data"))
colnames(df) = "filename"
```

### Iterate over file names and tidy the result

```{r, message=FALSE}
read_data = function(subject) {
  
  read_csv(paste0("./data/",subject))%>%
    janitor::clean_names() 
}

output = map_df(df[ ,1], read_data)

id = c(1:20)

df_problem1 = cbind(df, id, output) %>%
  mutate(filename = str_replace(filename, ".csv", ""))%>%
  separate(filename, into = c("control_arm", "subject_id"), sep = "_") %>%
  gather(key = week, value = observations, week_1:week_8) %>% 
  mutate(week = as.numeric(str_replace(week, "week_", "")),
         id = as.factor(id))
```

### Make a spaghetti plot

```{r}
df_problem1 %>%
  ggplot(aes(x = week, y = observations, color = id)) +
  geom_line() +
  facet_grid(~control_arm) +
  theme(legend.position = "bottom")+
  labs(
    x = "week",
    y = "value"
  )+
  ggtitle("Observations on each subject over time")
```

From the Spaghetti plot, we can find that the observations for subjects in experimental group increase over time while the observations for subjects in control group keep stable over weeks.

Problem 2

### Read data, add variable

```{r}
df2_raw = read.csv("./homicide-data.csv") %>% 
  janitor::clean_names()

df_problem2 = 
  df2_raw %>%
  mutate(city_state = paste(city, state, sep = ",")) 
```

The raw data contains `r ncol(df2_raw)` variables and `r nrow(df2_raw)` observations. The variables contain information about the id, report date, victim demographic character, city, state, location and disposition. The reported_date, lat and lon variables are numeric and the rest are factor variables.

### summarize total number and unsolved number of homicides

```{r}
df_summrize =
  df_problem2 %>% 
  group_by(city_state) %>% 
  summarize(total_homicide = n(),
            unsolved_homicide = sum(disposition == "Closed without arrest" | disposition == "Open/No arrest"))
```

### Estimate the proportion of unsolved homicides in Baltimore, MD

```{r}
Baltimore_homicide =
  df_problem2 %>% 
  filter(city_state == "Baltimore,MD") %>% 
  summarize(total_homicide = n()) 

Baltimore_unsolved_homicides =
  df_problem2 %>% 
  filter(disposition == "Closed without arrest" | disposition == "Open/No arrest" ) %>% 
  filter(city_state == "Baltimore,MD") %>% 
  summarize(total_homicide = n())

Baltimore_proportion_of_unsolved_homicides =   
  prop.test(Baltimore_unsolved_homicides[ ,1], Baltimore_homicide[    ,1]) %>% 
  broom::tidy() %>%
  janitor::clean_names()

Baltimore_proportion_of_unsolved_homicides %>% pull(estimate) 
Baltimore_proportion_of_unsolved_homicides %>% pull(conf_low)
Baltimore_proportion_of_unsolved_homicides %>% pull(conf_high)
```

### prop.test for each of the cities 

```{r, warning=F}
prop_test = function(x, y) {
  prop.test(x, y) %>% 
  broom::tidy() %>%
  janitor::clean_names()
}

estimate = function(n){
  df_filter = df_summrize %>%
  filter(city_state == n)

map2_df( df_filter$unsolved_homicide,df_filter$total_homicide,  prop_test)  
}

df_city_state = df_summrize %>% pull(city_state)

df_proportion = map_df(df_city_state, estimate)

df_summrize %>%
  mutate(estimate_proportion =  map(df_city_state, estimate)) %>% 
  unnest()
```








